Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-05-14 Manuscript/manuscript.Rmd
manuscript edits

[??? include icc for each component of table 1 with resolution]
The total number of genomic bins, which defined the dimensions of the data for modelling, was contingent upon the resolution of the contact matrix that cell line specific TADs were called on. Higher resolutions resulted in smaller unit bin widths, which corresponded to larger numbers of genomic bins (Table 1). For GM12878, there was an average of 12,214.1, 4,892.7, 2,450.9, and 1,227.5 bins created across chromosomes, for each resolution respectively. Likewise, the average number of bins, respective to resolution, were found to be similar on the K562 cell line (Supplementary Table 3).

As expected, the number of TADs called was related to resolution. Higher resolutions were found to result in a greater number of TADs called. For GM12878, an average of 365.5, 222.4, 111.9, and 49.1 TADs were called across chromosomes, for each respective resolution (Table 1). Average TADs called across chromosomes were found to be less on the K562 cell line at all resolutions (Supplementary Table 3). Although the downward trend was still present. As a result, a greater number of TADs corresponded to a greater number of TAD boundaries. For GM12878, the average number of TAD boundaries across chromosomes was found to be 1,254.6, 714.0, 364.4, and 165.3 for each resolution respectively (Table 1). Similar boundary profiles were exhibited on the K562 cell line (Supplementary Table 3).

>>>>

The total number of genomic bins, which defined the dimensions of the data for modelling, was contingent upon the resolution of the contact matrix that cell line specific TADs were called on. Higher resolutions resulted in smaller unit bin widths, which corresponded to larger numbers of genomic bins (Table 1). For GM12878, there was an average of 12,214.1, 4,892.7, 2,450.9, and 1,227.5 bins created across chromosomes, for each resolution respectively. Likewise, the average number of bins, respective to resolution, were found to be similar on the K562 cell line (Supplementary Table 3).

As expected, the number of TADs called was related to resolution. Higher resolutions were found to result in a greater number of TADs called. For GM12878, an average of 375.0, 228.4, 115.1, and 50.6 TADs were called across chromosomes, for each respective resolution (Table 1). Average TADs called across chromosomes were found to be less on the K562 cell line at all resolutions (Supplementary Table 3). Although the downward trend was still present. As a result, a greater number of TADs corresponded to a greater number of TAD boundaries. For GM12878, the average number of TAD boundaries across chromosomes was found to be 1,254.6, 714.0, 364.4, and 165.3 for each resolution respectively (Table 1). Similar boundary profiles were exhibited on the K562 cell line (Supplementary Table 3).
